\vskip-0.6in Trade Agreements in the Shadow of Lobbying\protect\footnote{Formerly circulated under the title ``Trade Agreements, Lobbying and Separation of Powers''}

### 2016-06-10 draft.tex
move uncertainty text from sec:choices to intro

The fact that zero contributions are predicted in equilibrium is not particularly satisfying. The addition of political uncertainty provides the missing realism, smooths the results and delivers additional intuition. I assume all actors are uncertain about the weight the median legislator in a non-unitary legislature places on the profits of the lobbying industry. This is meant to represent the idea that the lobbying and voting ``game'' that goes on within legislatures is often complex enough that none of the actors know precisely what the outcome will be---that is, no one can predict exactly which legislator will be the median and therefore what weight will be placed on import-industry profits at the time of the vote. For instance, perhaps a small number of lobbied legislators cannot deliver the votes of their non-lobbied colleagues with certainty. One can think of this uncertainty as an additional influence on the legislature's preferences about which all parties---executives, legislators and lobbies alike---are uncertain.

@@

Alternatively, the integration of the random variable $\ta$ can represent reduced-form modeling of political uncertainty arising from a complex decision-making process within a legislature. One can interpret $\ta$ as measuring uncertainty over the identity of the median legislator. \textbf{In this sense, the idea is similar to that of the probabilistic voting models that incorporate policy motivation such as Roemer (1997).} Here, it is meant to represent the idea that the lobbying and voting ``game'' that goes on within legislatures is often complex enough that none of the actors know precisely what the outcome will be---that is, no one can predict exactly which legislator will be the median and therefore what weight will be placed on import-industry profits at the time of the vote. Thus one way we can think about $\ta$ is as an additional influence on the legislature's preferences about which all parties---executives, legislators and lobbies alike---are uncertain. It is this interpretation of $\ta$ I take throughout this paper. %need to keep this paragraph and the next, or at least parts of it, to satisfy #22

One can conceptualize this uncertainty as being a result of the lobby's strategic choice to engage with only some key members of the legislature who wield significant influence but who cannot deliver policy decisions without the cooperation of others within the legislature, which is in turn uncertain. Different assumptions on $\ga(\cdot,\cdot)$ correspond to different institutional features and will affect optimal lobbying- and tariff-setting behavior. I make the following two basic assumptions on the weight on import-industry profits: %need to keep this paragraph and the previous, or at least parts of them, to satisfy #22

>>>>

\newpage
The fact that zero contributions are predicted in equilibrium is not particularly satisfying. The addition of political uncertainty provides the missing realism, smooths the results and delivers additional intuition. I assume all actors are uncertain about the weight the median legislator in a non-unitary legislature places on the profits of the lobbying industry. \textbf{Similar to probabilistic voting models that incorporate policy motivation such as Roemer (1997),} this represents the idea that the lobbying and voting ``game'' that goes on within legislatures is often complex enough that none of the actors know precisely what the outcome will be---that is, no one can predict exactly which legislator will be the median and therefore what weight will be placed on import-industry profits at the time of the vote.

\textbf{One can conceptualize this uncertainty as being a result of the lobby's strategic choice to engage with only some key members of the legislature who wield significant influence but who cannot deliver policy decisions without the cooperation of others within the legislature, which is in turn uncertain.} For instance, perhaps a small number of lobbied legislators cannot deliver the votes of their non-lobbied colleagues with certainty. One can think of this uncertainty as an additional influence on the legislature's preferences about which all parties---executives, legislators and lobbies alike---are uncertain.

@@
